### 2023-04-10 main/chapter_theory.tex
begin GMSB waffle

\subsection{Specific simplified models}
\TODO{add citations}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ `$\twoljets$'
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.
Many \atlas\ searches distribute their efforts across many simplified models.
This search patches just one part in the larger \atlas\ SUSY programme.

\paragraph{C1N2.}
`C1N2' is a restricted subset of the MSSM in which the only active SUSY
particles
are the lightest chargino ($\chargino_1$)
and the lightest two neutralinos ($\neutralino_1$, $\neutralino_2$).
The name `C1N2` is an abbreviation to
`Chargino 1' concatenated with `Neutralino 2'.
This model is active in the electroweak sector of the MSSM, which has received
increased interest in recent years because the LHC is more sensitive to models
in the strong sector.
Existing LHC have have already ruled out many strongly-interacting models
up to multi-$\eV[T]$ mass scales, but some viable phase space remains in the
electroweak sector.

Chargino-neutralino pairs could be produced in proton collisions via off-shell
$W$ boson propagators.
The targeted experimental signature is achieved by decays of these gauginos
to the $\neutralino_1$ LSP via emission of Standard Model particles.

\paragraph{GMSB.}
`GMSB' is \TODO{}.

\TODO{Cross-sections}

>>>>

\subsection{Specific simplified models}
\TODO{add citations}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ $\twoljets$
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.

Both of these simplified models are micro-examples of complete new theories
that offer solutions to the hierarchy
problem~\cite{Sakai:1981gr,SUSY-2018-02}.
Both models also conserve R-parity, so they satisfy constraints from proton
decay and introduce a stable, neutral dark matter candidate in their respective
LSPs~\cite{Ellis:1983ew}.
Many \atlas\ searches distribute their efforts across many simplified models;
this search embodies just one tile in the mosaic of \atlas's SUSY programme.

\paragraph{C1N2.}
`C1N2' is a restricted subset of the MSSM in which the only active SUSY
particles
are the lightest chargino ($\chargino_1$)
and the lightest two neutralinos ($\neutralino_1$, $\neutralino_2$).
The name `C1N2` is an abbreviation to
`Chargino 1' concatenated with `Neutralino 2'.
This model is active in the electroweak sector of the MSSM, which has received
increased interest in recent years because the LHC is more sensitive to models
in the strong sector.
Existing LHC results have have already ruled out many strongly-interacting
models up to multi-$\eV[T]$ mass scales, but some interesting phase space
remains in the electroweak sector.
We choose to study C1N2 to attend to this remaining phase space.

Chargino-neutralino pairs are produced in proton collisions via off-shell
$W$ boson propagators in this model.
The targeted experimental signature is achieved by decays of these gauginos
to the $\neutralino_1$ LSP via emission of Standard Model particles.

\paragraph{GMSB.}
As described earlier in Section~\ref{sec:theory_susy}, GMSB models offer a
general mechanism to break supersymmetry by communicating some symmetry
breaking down from high mass scales~\cite{Meade:2008wd,SUSY-2018-02}.
The specific GMSB model used in the \atlas\ $\twoljets$ search
(and referred to as simply GMSB in its context) is a simplified model that
captures broad patterns of plausible behaviours in an experimentally pragmatic
format.
Under this GMSB model, visible signatures are generated by decays higgsino-like
neutralinos to Standard Model particles and a gravitino LSP, specifically
$\neutralino_1 \to Z/h + \gravitino$.
% TODO diverse decay channels
% TODO diverse initial states

\subsubsection{Cross-sections}
\TODO{Cross-sections}
